### 2020-07-15 paper/sections/evaluation.tex
minor table 1

\begin{table*}[!t]
	\centering
	\caption{Experiment parameter}
	\label{tab: parameters}
	%     \begin{tabular}{llllll}
	\begin{tabular}{cccccc}
		\toprule
		Notation          & Value & & & Notation     & Value  \\ \midrule
		$c_{\rm ref}$ & 75    & & & $K$      & 1000   \\
		$\epsilon_{\min}$    & 0.02  & & & $p_0$    & 0.2    \\
		$\gamma$      & 0.95  & & & $\omega$ & -3   \\
		$ \mu_{\rm dec} $ & 0.99 & & & $ T $ & 5  \\
		$r_{\rm th}$  & 0.45   & & &   $ n  $  &  10      \\ 
		{\color{revise} $ \mathcal{A}_0 $} & {\color{revise}0.8} & & & {\color{revise}$ T_{\rm start} $} & {\color{revise}128} \\
		$ {\color{revise}\alpha} $ & {\color{revise}1} & & & {\color{revise}$ \beta $} & {\color{revise}1}  \\ \bottomrule
	\end{tabular}
	%	\vspace{-0.5cm}
\end{table*}

>>>>

\begin{table*}[!t]
	\centering
	\caption{Experiment parameter}
	\label{tab: parameters}
	%     \begin{tabular}{llllll}
	\begin{tabular}{cccccc}
		\toprule
		Notation          & Value & & & Notation     & Value  \\ \midrule
		$c_{\rm ref}$ & 75    & & & $K$      & 1000   \\
		$\epsilon_{\min}$    & 0.02  & & & $p_0$    & 0.2    \\
		$\gamma$      & 0.95  & & & $\omega$ & -3   \\
		$ \mu_{\rm dec} $ & 0.99 & & & $ T $ & 5  \\
		$r_{\rm th}$  & 0.45   & & &   $ n  $  &  10      \\ 
		{\color{revise} $ \mathcal{A}_0 $} & {\color{revise}0.8} & & & {\color{revise}$ T_{\rm start} $} & {\color{revise}128} \\
		$ {\color{revise}\alpha} $ & {\color{revise}1} & & & {\color{revise}$ \beta $} & {\color{revise}0}  \\ \bottomrule
	\end{tabular}
	%	\vspace{-0.5cm}
\end{table*}
